---
title: "T-Test Problem"
author: "Alexandra Shields-Knox"
date: "10 March, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_0$ : No difference between average years of education between those who voted and those who did not vote in 2012  

$H_A$ : There is a difference in the average years of education between those who voted in 2012 and those who did not. 

## Graphical Summary  

```{r}
plot(EDUC~VOTE12, data=Ourdata)
```

It appears that the average number of years of education is about same for both groups



## numerical summary

```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```

The mean is higher in the voted12 group than the no in 12 group.

## inferential test 


```{r}
t.test(EDUC ~ VOTE12, data=Ourdata)
```


The p-value is less than .05

##  Conclusion

The p-value from the t-test is less than 0.05, so we reject the null hypothesis. This test concludes that there is a difference between the average years of education between those who did and did not vote in 2012.